Specific taxa differentiate proximal and distal microbiota in the unprepped human colon

### 2017-06-20 submission/manuscript.Rmd
updated with pdf

---
title: 'Specific taxa differentiate proximal and distal microbiota in the unprepped
  human colon'
csl: mbio.csl
fontsize: 11pt
output:
  html_document: default
  pdf_document:
    includes: null
    keep_tex: yes
  word_document: default
geometry: margin=1.0in
bibliography: references.bib
---
\vspace{35mm}

@@

\newpage
\linenumbers

@@

```{r dependencies, echo=FALSE, warning = FALSE}
pack_used <- c('randomForest','ggplot2', 'pROC', 'knitr','dplyr','AUCRF', 'tidyr', 'caret', 'RColorBrewer', 'reshape2', 'wesanderson')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

>>>>

---
title: Specific taxa differentiate proximal and distal microbiota in the unprepped
  human colon
csl: mbio.csl
fontsize: 11pt
output:
  pdf_document:
    includes: null
    keep_tex: yes
    latex_engine: xelatex
  html_document: default
  word_document: default
geometry: margin=1.0in
bibliography: references.bib
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
---
\vspace{35mm}

@@

@@

```{r dependencies, echo=FALSE, warning = FALSE, message=FALSE}
pack_used <- c('randomForest','ggplot2', 'pROC', 'knitr','dplyr','AUCRF', 'tidyr', 'caret', 'RColorBrewer', 'reshape2', 'wesanderson')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

### 2017-06-20 submission/manuscript.tex
updated with pdf

\setlength{\droptitle}{-2em}
  \title{\emph{Specific taxa differentiate proximal and distal microbiota in the
unprepped human colon}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

\linenumbers

\begin{verbatim}
## randomForest 4.6-12
\end{verbatim}

\begin{verbatim}
## Type rfNews() to see new features/changes/bug fixes.
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'ggplot2'
\end{verbatim}

\begin{verbatim}
## The following object is masked from 'package:randomForest':
## 
##     margin
\end{verbatim}

\begin{verbatim}
## Type 'citation("pROC")' for a citation.
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'pROC'
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:stats':
## 
##     cov, smooth, var
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'dplyr'
\end{verbatim}

\begin{verbatim}
## The following object is masked from 'package:randomForest':
## 
##     combine
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:stats':
## 
##     filter, lag
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:base':
## 
##     intersect, setdiff, setequal, union
\end{verbatim}

\begin{verbatim}
## AUCRF 1.1
\end{verbatim}

\begin{verbatim}
## Loading required package: lattice
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'reshape2'
\end{verbatim}

\begin{verbatim}
## The following object is masked from 'package:tidyr':
## 
##     smiths
\end{verbatim}

@@

To identify OTUs that were distinct at each biogeographical site, we
constructed several Random Forest models built on OTU abundances. We
built the first model to classify the lumen versus mucosal samples for
the right and left sides, independently (Figure 4A). The constructed
model used ((Xopt)) features for the right and ((Xopt)) for the left.
The models performed well when classifying these samples (AUC = 0.797
and AUC = 0.980, respectively). The OTUs that were most predictive of
each site are identified by their greatest mean decrease in accuracy
when removed from the model. For distinguishing the right lumen and
mucosa, OTUs from the \emph{Bacteriodes}, \emph{Actinomyces},
\emph{Psuedomonas} and two OTUs from the \emph{Enterobacteraceae} genera
were differentially abundant (Figure 4B). The model classifying the left
lumen and mucosa identified OTUs from \emph{Turicibacter},
\emph{Finegoldia}, \emph{Peptoniphilus} and two OTUs from the
\emph{Anaerococcus} genera that could distinguish lumen from mucosal
samples (Figure 4C). These results indicate that there are fine
differences between the different sites of the colon, and that these can
be traced down to specific OTUs on each side.

@@

\includegraphics{submission/figure_1.pdf}

@@

\includegraphics{submission/figure_2.pdf}

@@

\includegraphics{submission/figure_3.pdf}

@@

\includegraphics{submission/figure_4.pdf}

@@

\includegraphics{submission/figure_5.pdf}

@@

\includegraphics{submission/figure_6.pdf}

>>>>

\setlength{\droptitle}{-2em}
  \title{Specific taxa differentiate proximal and distal microbiota in the
unprepped human colon}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers

@@

@@

To identify OTUs that were distinct at each biogeographical site, we
constructed several Random Forest models built on OTU abundances. We
built the first model to classify the lumen versus mucosal samples for
the right and left sides, independently (Figure 4A). The constructed
model used ((Xopt)) features for the right and ((Xopt)) for the left.
The models performed well when classifying these samples (0.8 and 1.0,
respectively). The OTUs that were most predictive of each site are
identified by their greatest mean decrease in accuracy when removed from
the model. For distinguishing the right lumen and mucosa, OTUs from the
\emph{Bacteriodes}, \emph{Actinomyces}, \emph{Psuedomonas} and two OTUs
from the \emph{Enterobacteraceae} genera were differentially abundant
(Figure 4B). The model classifying the left lumen and mucosa identified
OTUs from \emph{Turicibacter}, \emph{Finegoldia}, \emph{Peptoniphilus}
and two OTUs from the \emph{Anaerococcus} genera that could distinguish
lumen from mucosal samples (Figure 4C). These results indicate that
there are fine differences between the different sites of the colon, and
that these can be traced down to specific OTUs on each side.

@@

@@

@@

@@

@@

@@
